Extending the Advanced Forensic Format to accommodate Multiple Data Sources, Logical Evidence and Forensic Workflow

### 2009-03-13 paper/paper.tex
Started to implement encrypted stream.

\item Our implementation supports simultaneous access by multiple
  readers and writers. Our system allows concurrency by locking the
  file and interleaving write operations. Managing simultaneous
  writers is simplified through our update strategy which only writes
  new segments to the file, never modifying old segments.

\item AFF4 ``properties'' have specific semantics above and beyond
  normal segments. For example, AFF4 calls for all of the property
  segments associated with a file to be merged together. Furthermore,
  when updating the properties in a multi-volume Set, it is useful to
  write the same properties to each volume to ensure at least some of
the stream can be used even if some volumes are lost. Such
functionality is not present in standard ZIP64 implementations.
\end{itemize}

\section{Usage Scenarios}
In this section we describe how a FIF file format may be used in
various situations. Many of those can be solved using other forensic
file formats, but often in a more awkward way.

\subsubsection{Rapidly converting a set of DD images}
Many hardware devices are available to acquire hard disks in the
fields. These often produce a set of uncompressed images split at a
certain size. It is possible to construct a Map Stream which
seamlessly reassembles the logical image from all the individual disk
images. The new stream may be kept in its own volume and may be very
small.

If the images are split at exactly the same size its
possible to create a FIF archive consisting of a single Overlay
Stream, with a chunk\_size set to the size of each of the images. The
images can then be listed in order as external targets (e.g. {\em
target=file://disk1.dd}). This overlay can be created instantly
without needing to re-compress any of the images. In addition, digital
signatures can be generated for the whole stream or for each segment.

\subsubsection{Rapid conversion of EWF file sets}
Much existing evidence has been acquired using the EWF file
format. This format, similarly, consists of a series of chunks which
may be compressed, with interdispersed indexes. A tool such as
``ewf2fif'' is able to utilize the libewf library to create an Overlay
stream of the original image without the need to re-compress it. This
conversion is very quick and the resulting FIF file is very small -
each volume in the EWF file set is referenced through an external
target reference, and the Overlay Stream is built as an index of each
chunk location.

@@

With the FIF format, each of the disks can be acquired as a separate
Image Stream. Finally a tool such as PyFlag may be used to deduce the
RAID map, which can be appended to the FIF file as a Map Stream. This
Map Stream can then be opened by any tool without the tool needing to
have explicit support for RAID reassembling.

\subsubsection{Cryptographic management of evidence}
A FIF archive may hold multiple encrypted volumes, each in its own
Encrypted Stream. Each of those streams is encrypted using a different
master key, and therefore can have different passphrases, and can be
assigned to different users by encrypting the master key with
different X509 certificates. Its is also possible for users to create
non-encrypted volumes within the FIF file.

>>>>

\item Our implementation supports simultaneous access by multiple
  readers and writers. Since our system requires all metadata to be
  shared through the Universal Resolver, this lends itself to
  providing Universal Locking on a per Object basis. So for example,
  if one process wants to add a new segment into a Zip volume, they
  can lock it via the Resolver, add the segment and unlock the volume
  object in the resolver.
\end{itemize}

\section{Usage Scenarios}
In this section we describe how AFF4 may be used in various
situations. Many of those can be solved using other forensic file
formats, but often in a more awkward way.

\subsubsection{Rapidly converting a set of DD images}
Many hardware devices are available to acquire hard disks in the
fields. These often produce a set of uncompressed images split at a
certain size. It is possible to construct a Map Stream which
seamlessly reassembles the logical image from all the individual disk
images. The map stream may be kept in its own volume, or appended to
one (or all) of the image fragments.

@@

With the AFF4 format, each of the disks can be acquired as a separate
Image Stream. Finally a tool such as PyFlag \cite{pyflag_raid} may be
used to deduce the RAID map, which can be appended to the AFF4 file as
a Map Stream. This Map Stream can then be opened by any tool to get a
logical view of the RAID, without the tool needing to have explicit
support for RAID reassembling.

\subsubsection{In-place encryption of AFF4 volumes}
With the large size of a typical forensic image it is often difficult
to have to create a second copy of a volume which needs to be
encrypted. It is usually more convenient to encrypt the file in place,
overwriting the plain text data with the equivalent encrypted data.

This can be achieved using the technique shown in
Figure~\ref{inplace_crypto}. The first step is to encrypt the first
block from the front of the file and add it to the end of the archive
as a new encrypted segment. Then a ZipFile header is written to the
front which encapsulates the rest of the plain text volume. The plain
text volume is then encrypted in place. Finally a map stream is used
to re-map the first and second fragments into place, and a

\subsubsection{Cryptographic management of evidence}
An AFF4 archive may hold multiple encrypted volumes, each in its own
Encrypted Stream. Each of those streams is encrypted using a different
master key, and therefore can have different passphrases, and can be
assigned to different users by encrypting the master key with
different X509 certificates. Its is also possible for users to create
non-encrypted volumes within the FIF file.
